|

### 2022-05-24 paper_comparison/paper_comparison/paper_comparison.Rmd
explore patterns

@@

The previous section focuses on the change of effect size relative to the power of the visual test.

@@

lineup_info <- select(survey, type:answer, conventional_p_value, ori_difficulty, exp, exp_lineup_id, log_effect_size) %>%
  group_by(exp_lineup_id) %>% 
  filter(row_number() == 1) %>%
  ungroup()

@@

>>>>

<!-- sample 1, change values of a and b, plot the data  -->

@@

The previous section focuses on the change of effect size relative to the power of the visual test. However, effect size is only a one dimensional summarisation of parameters used in data simulation. Individual factor embedded in the simulation process should also be analysed.

In cubic model, two major factors that influencing the strength of the signal are $a$ and $b$. Figure \ref{fig:power-com-cubic-a} and \ref{fig:power-com-cubic-a} illustrates 30 different logistic regressions fit for different number of evaluations and different number of observations $n$. The regressor used in these models was $|a|/\sigma$ since the noise level $\sigma$ needed to be taken into account. From the figures, we can observe ...

@@

lineup_info <- select(survey, type:answer, conventional_p_value, ori_difficulty, exp, exp_lineup_id, log_effect_size) %>%
  group_by(exp_lineup_id) %>% 
  filter(row_number() == 1) %>%
  ungroup() %>%
  left_join(survey %>%
              count(exp_lineup_id) %>%
              rename(n_eval = n))

@@

```{r}
survey_single_pvalue <- survey %>%
  calc_p_value_multi(lineup_id = "exp_lineup_id", 
                     detected = "detect", 
                     n_sel = "num_selection",
                     comb = FALSE,
                     n_sim = 100000,
                     cache_env = env) %>%
  left_join(lineup_info, by = c("lineup_id" = "exp_lineup_id")) %>%
  mutate(reject = eval_p_value(p_value, tol = 1e-02))

```{r fig.height=6, fig.width=8}
# set.seed(20002)
# mod <- cubic_model(a = -3, b = 0, c = 1, sigma = 0.5, 
#                    x = rand_uniform(-1, 1), z = rand_uniform(-1, 1))

# fixed_sample <- mod$gen(100)
plot_list <- list()

for (a in seq(-3, 3, 1)) {
  for (b in seq(-3, 3, 1)) {

    set.seed(20002)

    mod <- cubic_model(a = a, b = b, c = 0, sigma = 0.5, 
                   x = rand_uniform(-1, 1), z = rand_uniform(-1, 1))

    plot_list[[paste(a, b, sep = "_")]] <- mod$gen(1000, fit_model = TRUE) %>%
    mod$plot("resid", remove_grid_line = TRUE, theme = theme_light(), remove_axis = TRUE) +
    ggtitle(glue::glue("a: {mod$prm$y$sym$a}, b: {mod$prm$y$sym$b}")) +
    ylim(c(-20, 20))
  }
}

patchwork::wrap_plots(plot_list, ncol = 7)
```

```{r fig.height=1.5, fig.width=8}
set.seed(20002)
mod <- cubic_model(a = -3, b = -3, c = 1, sigma = 0.5, 
                   x = rand_uniform(-1, 1), z = rand_uniform(-1, 1))

fixed_sample <- mod$gen(100)
plot_list <- list()

for (c in seq(0, 2, 0.5)) {
    mod$prm$y$sym$c <- c
    plot_list[[paste(c)]] <- mod$gen(100, fit_model = TRUE, 
                                     computed = list(e = fixed_sample$e,
                                                     x = fixed_sample$x,
                                                     z = fixed_sample$z)) %>%
    mod$plot("resid", remove_grid_line = TRUE, theme = theme_light(), remove_axis = FALSE) +
    ggtitle(glue::glue("c: {mod$prm$y$sym$c}")) 
}

patchwork::wrap_plots(plot_list, ncol = 5)
```

```{r}
plot_list <- list()

for (b in c(0, 0.5, 1, 1.5, 2, 2.5, 3, 10)) {

    set.seed(20002)
    mod <- heter_model(a = 1, b = b, x = rand_uniform(-1, 1))

    plot_list[[paste(b)]] <- mod$gen(1000, fit_model = TRUE) %>%
    mod$plot("resid", remove_grid_line = TRUE, theme = theme_light(), remove_axis = TRUE) +
    ggtitle(glue::glue("b: {b}"))
}

patchwork::wrap_plots(plot_list, ncol = 5)
```

```{r}
survey_single_pvalue %>%
  mutate(reject = as.numeric(reject)) %>%
  filter(n_eval >= 1) %>%
  ggplot() +
  geom_histogram(aes(log_effect_size, ..count../10), binwidth = 0.1) +
  geom_point(aes(log_effect_size, reject), alpha = 0.2) +
  geom_line(data = kernel_regression_cubic(sim_conv, 0.4), aes(x, reject), linetype = 2) +
  geom_line(data = kernel_regression_heter(sim_conv, 0.75), aes(x, reject), linetype = 2) +
  geom_smooth(aes(log_effect_size, reject), method = "glm", se = FALSE, method.args = list(family = binomial())) +
  facet_wrap(~type, scales = "free_x")
```

```{r}
sim_conv <- sim_conv %>%
  mutate(dis_b = cut(abs(b), breaks = c(0, 1, 2, 3)))

kernel_layer <- function(dis_b_index) {
  geom_line(data = kernel_regression_cubic(filter(sim_conv, as.numeric(dis_b) == dis_b_index), 
                                           0.4, 
                                           x = quote(abs(a))), 
            aes(x, reject, col = levels(sim_conv$dis_b)[dis_b_index]), 
            linetype = 2)
}

survey_single_pvalue %>%
  filter(type == "cubic") %>%
  mutate(reject = as.numeric(reject)) %>%
  mutate(dis_b = cut(abs(b), breaks = c(0, 1, 2, 3))) %>%
  filter(n_eval >= 1) %>%
  ggplot() +
  # geom_histogram(aes(log_effect_size, ..count../10), binwidth = 0.1) +
  geom_point(aes(abs(a), reject), alpha = 0.2) +
  kernel_layer(1) +
  kernel_layer(2) +
  kernel_layer(3) +
  geom_smooth(aes(abs(a), reject, col = dis_b), method = "glm", se = FALSE, method.args = list(family = binomial())) +
  facet_grid(n~e_sigma, scales = "free_x") +
  labs(col = "abs(b)")
```

```{r}
